\mbox{[}1\mbox{]} E. Michielssen and A. Boag, \char`\"{}\+A multilevel matrix decomposition algorithm for analyzing scattering from large structures,\char`\"{} IEEE Trans. Antennas Propag., vol. 44, pp. 1086-\/1093, 1996.

\mbox{[}2\mbox{]} H. Guo, J. Hu, and E. Michielssen, \char`\"{}\+On MLMDA/butterfly compressibility of inverse integral operators,\char`\"{} IEEE Antenn. Wireless Propag. Lett., vol. 12, pp. 31-\/34, 2013.

\mbox{[}3\mbox{]} Y. Li, and H. Yang, \char`\"{}\+Interpolative butterfly factorization,\char`\"{} SIAM Journal on Scientific Computing, vol. 39, pp. 503-\/531, 2016.

\mbox{[}4\mbox{]} H. Guo, Y. Liu, J. Hu, and E. Michielssen, \char`\"{}\+A butterfly-\/based direct integral equation solver using hierarchical LU factorization for analyzing scattering from electrically large conducting objects\char`\"{}, IEEE Trans. Antennas Propag., 2017.

\mbox{[}5\mbox{]} Y. Liu, H. Guo, and E. Michielssen, \char`\"{}\+A HSS matrix-\/inspired butterfly-\/based direct solver for analyzing scattering from two-\/dimensional objects\char`\"{}, IEEE Antennas\+Wireless Propag. Lett., 2017.

\mbox{[}6\mbox{]} H. Guo, Y. Liu, J. Hu, E. Michielssen, \char`\"{}\+A butterfly-\/based direct solver using hierarchical LU factorization for Poggio-\/\+Miller-\/\+Chang-\/\+Harrington-\/\+Wu-\/\+Tsai equations\char`\"{}, Microwave and Optical Technology Letters, 2018, 60\+:1381-\/1387.

\mbox{[}7\mbox{]} Y. Liu, W. Sid-\/\+Lakhdar, E. Rebrova, P. Ghysels, X. Sherry Li, \char`\"{}\+A parallel hierarchical blocked adaptive cross approximation algorithm\char`\"{}, ar\+Xiv e-\/prints, January 1, 2019.

\mbox{[}8\mbox{]} Y. Liu, H. Yang, \char`\"{}\+A hierarchical butterfly LU preconditioner for two-\/dimensional electromagnetic scattering problems involving open surfaces\char`\"{}, arxiv e-\/preprint, February 1, 2019. 